Covariates analysis of MSBB RNASeq data

### 2016-01-26 code/Rmd/MSSM_RNASeq.Rmd
Minor modifications

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(Comparison, hgnc_symbol) %>%
  group_by(Comparison) %>%
  summarise(nDiffExp = length(unique(hgnc_symbol)), 
            DiffExpGenes = paste(unique(hgnc_symbol), collapse = ','))

@@

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
```
|  *Results*            |  *SynapseID*                    |
|  -------              |   ---------                     |
|  Covariates           |  `r covar_obj$properties$id`    |
|  Residual Expression  |  `r expr_obj$properties$id`     |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |

>>>>

tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(Comparison, hgnc_symbol) %>%
  group_by(Comparison) %>%
  dplyr::summarise(nDiffExp = length(unique(hgnc_symbol)), 
            DiffExpGenes = paste(unique(hgnc_symbol), collapse = ','))

@@

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
```
|  *Results*            |  *SynapseID*                    |
|  -------              |   ---------                     |
|  Covariates           |  `r covar_obj$properties$id`    |
|  Residual Expression  |  `r expr_obj$properties$id`     |
|  Differential Expression  |  `r dexp_obj$properties$id`      |
